### 2023-08-22 paper/app-faser.tex
app A

\section{Impact of FASER$\nu$ Run III measurements}
\label{app:fasernu_runIII_impact}

%
Fig.~\ref{fig:profiling_FASERv2_vs_FASERv} shows a comparison of the impact 
that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
the improvement in precision obtainable with FASER$\nu$2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
\caption{
A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
assuming only statistical uncertainties in the case of both experiments.
}
\label{fig:profiling_FASERv2_vs_FASERv}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\clearpage
\section{Impact of FASER$\nu$ Run III measurements}
\label{app:fasernu_runIII_impact}

The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
can also be used in the case of the FASER$\nu$ pseudo-data, generated under the
assumption a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
that FASER$\nu$ will have recorded around 500 and 1500 electron- and muon-neutrinos
respectively corresponding to deep-inelastic scattering events, of which around 100
and 250 respectively are associated to charm-tagged events.
%
These projected event rates can be compared with the expectations
for FASER$\nu$2, which predicts an increase in statistics of up to two orders
of magnitude.

Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
Fig.~\ref{fig:FASERnu2_baseline} now between that projected PDF impact of FASER$\nu$2 and that of
FASER$\nu$, in the latter
case for an integrated luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
%
The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
%
The striking differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
the key importance of realising the FPF in order to exploit the full physics potential enabled 
by LHC neutrinos for QCD and hadron structure studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
  the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
  case assuming the Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
}
\label{fig:FASERnu2_vs_FASERnu}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It should be emphasized that the lack of PDF sensitivity displayed in Fig.~\ref{fig:FASERnu2_vs_FASERnu}
does not imply that measuring DIS structure functions at FASER$\nu$ will not provide new information.
%
First of all, our procedure assumes perfect compatibility between current data and the projected DIS
neutrino measurements at the LHC, something which remains to be demonstrated experimentally.
%
Second, FASER$\nu$ still covers a region of neutrino energies unexplored by previous experiments, hence providing
a new validation of our QCD calculations and of neutrino interactions at the TeV scale.
%
Third, it would represent a non-trivial proof-of-concept that LHC neutrino differential measurements can be
unfolded to the cross-section level such that they can be used in  theoretical
interpretations, paving the way and demonstrating the feasibility of subsequent neutrino DIS
measurements at the FPF experiments.

### 2023-08-22 paper/sec-introduction.tex
app A

The outline of this paper is as follows.
%
First, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
adopted to generate projections for DIS structure functions associated to
LHC neutrino scattering, including the modelling of experimental systematic
uncertainties.
%
Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
for the calculation of DIS structure functions and the methodology adopted
to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
%
The projected impact of these structure functions on proton and nuclear
PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
%
Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
directions for follow-up research.

>>>>

The outline of this paper is as follows.
%
First, in Sect.~\ref{sec:dis_pseudodata} we describe the procedure
adopted to generate projections for DIS structure functions associated to
LHC neutrino scattering, including the modelling of experimental systematic
uncertainties.
%
Then in Sect.~\ref{sec:settings} we discuss the theoretical settings used
for the calculation of DIS structure functions and the methodology adopted
to account for the constraints of LHC neutrino DIS data on proton and nuclear PDFs.
%
The projected impact of these structure functions on proton and nuclear
PDFs is quantified in Sects.~\ref{sec:protonPDFs} and~\ref{sec:nuclearPDFs} respectively.
%
Finally we summarise in Sect.~\ref{sec:summary} and consider some possible
directions for follow-up research.
%
Additional impact results are collected in two appendices:
App.~\ref{app:fasernu_runIII_impact} studies the possible PDF impact
of FASER$\nu$ Run III measurements, and App.~\ref{app:nPDF_impact_appendix}
quantifies the stability of the nuclear PDF projections with respect
of variations of its inputs.

### 2023-08-22 paper/sec-summary.tex
app A

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement.
%
We thank specially Felix Kling for may useful discussions in the course
of the project.
%
We thank Akitaka Ariga and Tomoko Ariga for information
concerning FASER$\nu$2, Milind Diwan,
Wenjie Wu and Steven Linden concerning FLArE,
and Antonia di Crescenzo concerning AdvSND.

>>>>

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement along the course of this project.
%
We thank specially Felix Kling for may useful discussions in the course
of the project.
%
We thank Akitaka Ariga and Tomoko Ariga for discussion
concerning FASER$\nu$2, Milind Diwan,
Wenjie Wu and Steven Linden concerning FLArE,
and Antonia di Crescenzo concerning AdvSND.
